International Relations are a Social Network:\\ A Latent Network Approach for Global Politics

### 2017-10-21 paper/4_app.tex
fix rose out samp

\begin{figure}
\centering   
\subfigure[AUC]{\label{fig:reitaucpr}\includegraphics[width=65mm]{reiter_auc_outsamp.pdf}}
\subfigure[Precision and Recall]{\label{fig:reitpr}\includegraphics[width=65mm]{reiter_pr_outsamp.pdf}}
\caption{Assessments of out-of-sample predictive performance for Reiter \& Stam (2003) using ROC curves and PR curves.}
\end{figure}
\FloatBarrier

>>>>

\begin{figure}
	\centering   
	\subfigure[AUC]{\label{fig:reitaucpr}\includegraphics[width=.45\textwidth]{reiter_auc_outsamp.pdf}}
	\subfigure[Precision and Recall]{\label{fig:reitpr}\includegraphics[width=.45\textwidth]{reiter_pr_outsamp.pdf}}
	\caption{Assessments of out-of-sample predictive performance for Reiter \& Stam (2003) using ROC curves and PR curves.}
\end{figure}
\FloatBarrier
